What's hot and what's not:\\Windowed developer topic analysis

### 2009-04-12 lda-paper.tex
minor spell checks

We carried otu \emph{global topic analysis} on MaxDB 7.500 and
compared this against our windowed topic analysis.  To produce
figure~\ref{fig:statictopics}, we extracted 20 topics and plotted the
number of messages per month that were related to that topic. We found
was that one topic would often dominate the results, as shown in the
third row of Figure \ref{fig:statictopics}, while messages related to
other topics did not appear often.
% This technique seems useful if the 20 extracted topics are relevant
% and useful, that said one weakness of this approach is that documents
% for a topic might only occur in one time window, yet we are tracking
% messages that could be related to it over the entire lifetime of the
% project.
This approach seems reasonable if most of the extracted topics are of
broad interest during most of the development process.  However, it
may be that some topics are of strong interest but only briefly; in
such a case, a windowed topic analysis gives a much stronger
indication of the fleeting importance of such topics, and can help to
put such a topic into its proper context.

@@

Adding and removing stop words produced different results. Our choice
of stopwords could be biased, and could affect the results.
%, and our bias for or against such stop words could affect
%the results.

>>>>

We carried out \emph{global topic analysis} on MaxDB 7.500 and
compared this against our windowed topic analysis.  To produce
figure~\ref{fig:statictopics}, we extracted 20 topics and plotted the
number of messages per month that were related to that topic. We found
was that one topic would often dominate the results, as shown in the
third row of Figure \ref{fig:statictopics}, while messages related to
other topics did not appear often.
% This technique seems useful if the 20 extracted topics are relevant
% and useful, that said one weakness of this approach is that documents
% for a topic might only occur in one time window, yet we are tracking
% messages that could be related to it over the entire lifetime of the
% project.
This approach seems reasonable if most of the extracted topics are of
broad interest during most of the development process.  However, it
may be that some topics are of strong interest but only briefly; in
such a case, a windowed topic analysis gives a much stronger
indication of the fleeting importance of such topics, and can help to
put such a topic into its proper context.

@@

Adding and removing stop words produced different results. Our choice
of stop words could be biased, and could affect the results.
%, and our bias for or against such stop words could affect
%the results.
